### 2015-04-28 evaluation.tex
update

We can see that, in general, \whoop reports (many) more races than \corral. This is expected because \whoop over-approximates the original driver for soundness: if a race exists, the tool will report it (assuming tool and model correctness), but \whoop can also report false races. On the other hand, \corral reports only real races, but does that under pre-defined bounds. It is worthwhile to note that a common problem for \corral (especially when analyzing drivers) is loop coverage. To deal with this we enable the over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice.

@@

\noindent
\textbf{Granularity of Context-Switches}\xspace\xspace Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks. All reported times are in seconds and averages of three runs. \corral was given a time budget of 2 hours (T.O. denotes a tool timeout) and a context-switch bound (csb) of 2, 5 and 9. By default, \corral instruments context-switches (i.e. \texttt{yield}) in all visible operations (denoted by \yieldall in the table). \whoop + \corral, instead, uses two different context-switch instrumentation granularities (see Section~\ref{whoop:bugfinding}): \yieldcoarse and \yieldmr.

>>>>

We can see that, in general, \whoop reports (many) more races than \corral. This is expected because \whoop over-approximates the original driver for soundness: if a race exists, the tool will report it (assuming tool and model correctness), but \whoop can, and does, report false races. On the other hand, \corral reports only real races, but does that under pre-defined bounds. It is worthwhile to note that a common problem for \corral (especially when analyzing drivers) is loop coverage. To deal with this we enable the over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice.

@@

\noindent
\textbf{Granularity of Context-Switches}\xspace\xspace Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks. All reported times are in seconds and averages of three runs. \corral was given a time budget of 8 hours (T.O. denotes a tool timeout) and a context-switch bound (csb) of 2, 5 and 9. By default, \corral instruments context-switches (i.e. \texttt{yield}) in all visible operations (denoted by \yieldall in the table). \whoop + \corral, instead, uses two different context-switch instrumentation granularities (see Section~\ref{whoop:bugfinding}): \yieldcoarse and \yieldmr.
